Looking at Non-Linear Dimension Reductions as Models in the Data Space

### 2025-02-04 paper.qmd
Updated Figure 2

axes_obj <- gen_axes(  
  proj = projection * 6,
  limits = 0.5,
  axis_pos_x = -0.35,
  axis_pos_y = -0.35,
  axis_labels = names(scaled_two_curvy_data),
  threshold = 0)

>>>>

axes_obj <- gen_axes(  
  proj = projection * 6,
  limits = 0.5,
  axis_pos_x = -0.3,
  axis_pos_y = -0.3,
  axis_labels = names(scaled_two_curvy_data),
  threshold = 0)
